EffDose_Contrast_Graphics

### 2019-08-27 R Files/ED_Contrast_Graphics.Rmd
edits

box_ScannerContrast <- ggplot(PE, aes(x = CT.Type, y = Contrast.Given, fill = CT.Type)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue", "dodgerblue" ,"mediumblue" ,"navyblue")) +
                ylab("Contrast (mL)") + 
                xlab("Scanner Type") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Type of Scanner Used")

>>>>

box_ScannerContrast <- ggplot(PE, aes(x = CT.Type2, y = Contrast.Given, fill = CT.Type)) +
                geom_boxplot() +
                scale_fill_manual(values = c("lightblue", "dodgerblue" ,"mediumblue" ,"navyblue")) +
                ylab("Contrast (mL)") + 
                xlab("Scanner Type") +
                theme(legend.position = "none") +
                ggtitle("Contrast Administered by Type of Scanner Used")
